\begin{thebibliography}{99}
\bibitem{} Halzen F., Martin A.D.: {\em Quarks and Leptons: An Introductory
  of Course in Modern Particle Physics}, John Wiley and Sons, 1984.
\bibitem{} Rafelski J.: {\em 21st Rencontres de Moriond}, Les Arcs, 1983
\bibitem{} Jacob M.: {\em In Search of Quark Gluon Plasma}, Springer Verlag,
  1985
\bibitem{} Davies J.P.: {\em Particles in Ultra-Relativistic Proton-Tungsten
  Collision at 200 GeV/c per Nucleon}, PhD Thesis, School of Physics and Space
  Research, Faculty of Sciense, The University of Birmingham, November 1995

\bibitem{} Bayes, C.A.: {\em Strange Particle Production in
  Sulphur-Sulphur Interactions at 200
  GeV/c per Nucleon}, PhD Thesis, RAL-TH-95-008, School of Physics and Space
  Research, Faculty of Sciense, The University of Birmingham, March 1995.
\bibitem{} Barnes, P. R.: {\em Production of Strange and Multistarnge
  Baryons in Ultrarelativistic Heavy Ion Collision}, PhD Thesis, RALT-169,
  Scool of Physics and Space Research, Faculty of Science, The University of
  Birmingham, June 1993.
\bibitem{} Matsui T.: {\em Phys. Lett. {\bf B178} 1986 416.}
\bibitem{} Bordalo P.: {\em NA38 Collaboration}, Proc. XXII Rencontres de
  Moriond, 1988.
\bibitem{} Rafelski J. and Hagedorn R.: {\em Statistical Mechanics of Quarks
  and  Hadrons}, North Holland, Amsterdam 1981.

\bibitem{} Evans, D.: {\em  Strange and Multistarnge Baryon and Antibaryon
  Production in Sulphur-Tungsten Interactions at 200 GeV/c per Nucleon}, PhD
  Thesis, RALT-130, School of Physics and Space Research, The University of
  Birmingham, April 1992.
\bibitem{} Ellis J. and Heinz U.: {\em Phys. Lett. {\bf B233} 1989 167.}
\bibitem{} Eggers H.C. and Rafelski J.: {\em Int. J. of Mod. Phys. A,
  Vol.6, No. 7 1991 1067.}
\bibitem{} Koch P., Müller B. and Rafelski J.: {\em Phys. Rep. 142 1986
  167.}
\bibitem{} Hove van L.: {\em Z. Phys. {\bf C27} 1985 135.}
\bibitem{} Csernai L.P., Holme A.K. and Staubo E.F.: {\em What can we learn
  from $p_{T}$ distribution in relativistic heavy ion collisions ?}, Plenum
  Press, 1989.
\bibitem{} The WA85 Coll., Abatzis et al.: {\em Phys. Lett. {\bf B244} 1990
  130.}
\bibitem{} Lassalle J. C. at al.: {\em DD/EE/79-2 (TRIDENT manual)}
\bibitem{} Eggers H. C. and Rafelski J.: {\em Int. J. of Mod. Phys. A, vol.
  6, no. 7 (1991) 1067}
\bibitem{} Schukraft J.: {\em CERN-PPE/91-04}
\bibitem{} Kinson J. B.: {\em Nuclear Physics {\bf A590} (1991) 317c.-332c.}
\bibitem{} Lietava R.: {\em J. Phys. G: Nucl. Part. Phys.{\bf 25}
  (1999) 181-188},
\bibitem{} HELIOS Collaboration {\em Phys. Lett. {\bf B 296} (1992) 277}
\bibitem{} NA35 Collaboration {\em Z. Phys. {\bf C 64} (1994) 197-200}


\bibitem{} Helstrup, H.: {\em Starnge and Non-Strange Baryon Production
  in Ultrarelativistic Sulphur-Tungsten and Sulphur-Sulphur Collision}, PhD
  Thesis, Fysisk institutt, Universitetet i Bergen, April 1993.

\bibitem{} Lovhoiden, G.: {\em Heavy Ion Collision at High Energies}, in
  Kompendium FYS338 (UiB) og FYS374 (UiO), 1996.
\end{thebibliography}
